---
title: "Southern women"
author: "Emma Livingston"
date: "2/25/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(igraph)
library(readr)
```

Data source: [moreno.ss.uci.edu](http://moreno.ss.uci.edu/davis.dat)

```{r load_data}
#Create a matrix (person by event) of the women and events
southern_women <- as.matrix(read.csv("data/southern_women.csv", row.names = 1))
```

```{r}
#create a person by person matrix
person_net <- southern_women %*% t(southern_women)

#create an event by event matrix
event_net <- t(southern_women) %*% southern_women

#set the diagonals of these matrices as NA
diag(event_net) <- NA
diag(person_net) <- NA
```

```{r}
#Create a graph adjacency list by person that is weighted and undirected
person_g <- graph.adjacency(person_net,mode="undirected",
                            weighted=NULL, diag=FALSE)


#Create a graph adjacency list by event that is weighted and undirected
event_g <- graph.adjacency(event_net, weighted=TRUE,
                           mode="undirected", diag=FALSE)

```

```{r}
#create a layout schema and weight for the event graph
la <- layout.fruchterman.reingold(event_g)
e_wt <- get.edge.attribute(event_g, "weight")
```

```{r}
#plot the events as a pdf
pdf(file="figures/group-view.pdf", width=10, height=10)
plot(event_g, layout=la, vertex.size=15,edge.width=e_wt,
     vertex.label=V(event_g)$name)
```

```{r}
#plot the events as a png
png(file="figures/group-view.png", width=1000, height=1000, res=150)
plot(event_g, layout=la, vertex.size=15,edge.width=e_wt,
     vertex.label=V(event_g)$name)

```

```{r}
#plot the people as a pdf
pdf(file="figures/southern_women-network.pdf", width=22, height=17,pointsize=8)
la2 <- layout.fruchterman.reingold(person_g)
e_wt2 <- get.edge.attribute(person_g, "weight")
plot(person_g, layout=la2, vertex.size=3,edge.width=0.1,
     vertex.label=V(person_g)$name)

```

```{r}
#plot the people as a png
png(file="figures/southern_women-network.png", width=2200, height=1700, res=150)
la3 <- layout.fruchterman.reingold(person_g)
e_wt3 <- get.edge.attribute(person_g, "weight")
plot(person_g, layout=la3, vertex.size=3,edge.width=0.1,
     vertex.label=V(person_g)$name)

```

```{r}
#person by person matrix in the other direction
person2_net <- southern_women %*% t(southern_women)

#make the diagonal NA
diag(person2_net) <- NA

#transposed person graph
person2_g <- graph.adjacency(person2_net, mode="undirected", weighted=TRUE, diag=FALSE)

#transposed layout and edge weight
la4 <- layout.fruchterman.reingold(person2_g)
e_wt4 <- get.edge.attribute(person2_g, "weight")
```

```{r}
#transposed person graph as pdf
pdf(file="figures/person-weighted-view.pdf", width=20, height=20)
plot(person2_g, layout=la4, vertex.size=15,edge.width=e_wt4,
     vertex.label=V(person2_g)$name)
```

```{r}
#transposed person graph as png
png(file="figures/person-weighted-view.png", width=2000, height=2000, res=150)
plot(person2_g, layout=la4, vertex.size=15,edge.width=e_wt4,
     vertex.label=V(person2_g)$name)
```

# Centrality

Betweenness centrality: the measure of centralit yin a graph based on the shortest paths. For every pari of vertices in a connected graph, there exists at least one shortest path between the vertices such that either the number of edges that the path passes through or the sum of the weights of the edges is minimized. The betweenness centrality for each vertex is the number of these shortest paths that pass through the vertex. -- [Wikipedia Betweenness centrality](https://en.wikipedia.org/wiki/Betweenness_centrality)


```{r betweenness}
#calculate betweenness
btwn_person <- betweenness(person_g)
names(btwn_person) <- V(person_g)$name
ind <- order(-btwn_person)
btwn_person[ind][1:10]
btwn_person[ind]
```

MOST POPULAR: Theresa, Evelyn, Nora, Ruth, Sylvia

LEAST POPULAR: Flora, Olivia, Dorothy, Helen, Nora

```{r eigenvector}
cent_eig <- evcent(person_g)
names(cent_eig$vector) <- V(person_g)$name
ind <- order(-cent_eig$vector)
cent_eig$vector[ind][1:10]
```

MOST POPULAR: Theresa, Evelyn, Sylvia, Brenda, Laura

LEAST POPULAR: Flora, Olivia, Charlotte, Pearl

```{r kleinberg_authority}
cent_klein <- authority.score(person_g)
names(cent_klein$vector) <- V(person_g)$name
ind <- order(-cent_klein$vector)
cent_klein$vector[ind][1:10]

```

MOST POPULAR: Theresa, Evelyn, Sylvia, Brenda, Laura

LEAST POPULAR: Flora, Olivia, Charlotte, Pearl

```{r bonacich_power}
cent_bonpow <- bonpow(person_g, exponent=1)
names(cent_bonpow) <-  V(person_g)$name
ind <- order(cent_bonpow)
cent_bonpow[ind][1:10]

```

Losest Bonacich Power centrality: Pearl, Myrna, Dorothy, Evelyn, Frances

```{r}
ind <- cent_bonpow < -1.35

col_vec <- rep("")

pdf(file="figures/southern_women-network-reduced.pdf", width=22, height=17,pointsize=8)
person_g_copy <- person_g
la5 <- layout.fruchterman.reingold(person_g_copy)
plot(person_g_copy, layout=la5, vertex.size=3,
     vertex.label=V(person_g_copy)$name)
```

```{r}
png(file="figures/southern_women-network-reduced.png", width=2200, height=1700, res=140)
la6 <- layout.fruchterman.reingold(person_g_copy)
plot(person_g_copy, layout=la6, vertex.size=3,
     vertex.label=V(person_g_copy)$name)

```

```{r}
png(file="figures/southern_women-test.png", width=2200, height=1700)
com <- spinglass.community(person_g, spins=5)
V(person_g)$color <- com$membership+1
person_g <- set.graph.attribute(person_g, "layout", layout.fruchterman.reingold(person_g))
plot(person_g)

```

```{r}
png(file="figures/southern_women-test.png", width=2000, height=1000)
lay <- layout.fruchterman.reingold(person_g)
pr_id <- 200
# Plot the eigevector and betweenness centrality
par(mfrow=c(1,2))
plot(bonpow(person_g, exponent=1), betweenness(person_g))

```

```{r}
# e_rank <- rank(-evcent(person_g)$vector)
# b_rank <- rank(-betweenness(person_g))
# c_rank <- rank(-bonpow(person_g, exponent=1))
# s_top <- c_rank < 10 | b_rank < 10
# text(bonpow(person_g)[s_top], betweenness(person_g)[s_top], cex=0.6, pos=4, labels=V(person_g)$name[s_top])
# V(person_g)[pr_id]$color <- "yellow"
# E(person_g)$color="grey95"
# plot(person_g, layout=lay, vertex.size=2,
#        vertex.label.cex=0.6, vertex.label=V(person_g)$name)

```

